Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-09 Draft/acknowledgements.tex
Lots of corrections and improvements

 We thank ...
Acknowledgement of VBSCAN COST action.

>>>>

The authors would like to acknowledge the contribution of the COST Action CA16108 which initiated this work.
Moreover, this work was supported by sveral STSM Grant from the COST Action CA16108.

BB, AD, and MP acknowledge financial support by the
German Federal Ministry for Education and Research (BMBF) under
contract no.~05H15WWCA1 and the German Science Foundation (DFG) under
reference number DE 623/6-1.

### 2018-02-09 Draft/contributions.tex
Some changes in sections 4.3 and 5.2
Minor changes on draft, mostly typos
Lots of corrections and improvements

At tree level, there are three contributions to the $\PW^+\PW^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$, and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$.
In the present section, the cross sections and distributions are obtained without applying the VBS cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
In Tab.~\ref{tab:LOscanXsec}, the cross sections of the three contributions are displayed.
The EW, QCD, and interference contributions amount to $57\%$, $37\%$, and $6\%$ of the total inclusive cross section, respectively.
The QCD contribution does not posses external gluons due to charge conservation.
Thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve gluon exchange in the $t/u$-channel between the quark lines.
This results in a small contribution although the VBS cuts have not been imposed.
The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions).

\begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c|c}
        Order & $ \mathcal{O}(\alpha^6)$ & $\mathcal{O}(\alphas^2\alpha^4)$ & $\mathcal{O}(\alphas\alpha^5)$ \\
        \hline
        \hline
        $\sigma[\rm{fb}]$ & $ 2.292 \pm 0.002 $ & $ 1.477 \pm 0.001 $ & $ 0.223 \pm 0.003 $ \\
%         {\sc Xxx}&  $ \pm $ & $ \pm $ & $ \pm $
    \end{tabular}
    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process.
    These results are for the set-up described in Sec.~\ref{subsec:inputpar}, dropping the $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ cuts.}
\end{table}

In Fig.~\ref{fig:mjjdyjj_1d} these three contributions are shown separately and summed in the differential distribution of the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
The EW contribution peaks around an invariant mass of about $80\GeV$.
These are due to diagrams where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
Note that these contributions are not present in calculations relying on the VBS approximation.
Also, the EW contribution becomes dominant for di-jet invariant mass larger than $500\GeV$ and for jet rapidity difference larger than $2.5$.

@@

This can also be seen in Fig.~\ref{fig:mjjdyjj_2d_LO} where the three contributions are displayed as a function of the di-jet invariant mass and jet rapidity difference.
Again, it is obvious that the region with low di-jet invariant mass and low jet-rapidity difference should be avoided.
This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and $|\Delta y_{\Pj\Pj}| > 2$ for our inclusive study (see below).
Finally, let us notice that the choice $m_{\Pj\Pj} > 500\GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ made by the experimental collaborations is well motivated in order to enhance the EW contribution over its irreducible backgrounds.
This is are the cuts used in Sec.~\ref{subsec:LOfiducial}.

>>>>

At tree level, there are three contributions to the $\PW^+\PW^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$, and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$.
In the present section, the cross sections and distributions are obtained without applying the VBS cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
In Tab.~\ref{tab:LOscanXsec}, the cross sections of the three contributions are reported.
The EW, QCD, and interference contributions amount to $57\%$, $37\%$, and $6\%$ of the total inclusive cross section, respectively.
The QCD contribution does not posses external gluons due to charge conservation.
Thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve gluon exchange in the $t/u$-channel between the quark lines.
This results in a small contribution although the VBS cuts have not been imposed.
The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions).

\begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c|c}
        Order & $\mathcal{O}(\alpha^6)$ & $\mathcal{O}(\alphas^2\alpha^4)$ & $\mathcal{O}(\alphas\alpha^5)$ \\
        \hline
        \hline
        $\sigma[\rm{fb}]$ & $ 2.292 \pm 0.002 $ & $ 1.477 \pm 0.001 $ & $ 0.223 \pm 0.003 $ \\
%         {\sc Xxx}&  $ \pm $ & $ \pm $ & $ \pm $
    \end{tabular}
    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the three contributions to the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
    These results are for the set-up described in Sec.~\ref{subsec:inputpar}, dropping the $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ cuts.}
\end{table}

In Fig.~\ref{fig:mjjdyjj_1d} these three contributions are shown separately and summed in the differential distribution of the di-jet invariant mass $m_{\Pj\Pj}$ and the rapidity difference $|\Delta y_{\Pj\Pj}|$.
In the distributions in the di-jet invariant mass (left), one can observe that the EW contribution peaks around an invariant mass of about $80\GeV$.
These are due to diagrams where the two jets originate from the decay of a W boson (see middle and right diagrams in Fig.~\ref{diag:LO}).
Note that these contributions are not present in calculations relying on the VBS approximation.
Also, the EW contribution becomes dominant for di-jet invariant mass larger than $500\GeV$.
The same holds true for jet rapidity difference larger than $2.5$ (right).
This clearly explains why these two observables are used to enhanced the EW contribution over the QCD one.
In particular, in order to have a large EW contribution, rather exclusive cuts are required.

@@

This can also be seen in Fig.~\ref{fig:mjjdyjj_2d_LO} where the three contributions are displayed as a function of the di-jet invariant mass and jet rapidity difference.
Again, it is obvious that the region with low di-jet invariant mass and low jet-rapidity difference should be avoided.
This motivates in particular the choice of $m_{\Pj\Pj} > 200\GeV$ and $|\Delta y_{\Pj\Pj}| > 2$ for our inclusive study (see below).
Finally, let us notice that the choice $m_{\Pj\Pj} > 500\GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ made by the experimental collaborations is well motivated in order to enhance the EW contribution over its irreducible backgrounds.
These are the cuts used in Sec.~\ref{subsec:LOfiducial}.

### 2018-02-09 Draft/crosssectionLO.tex
Lots of corrections and improvements

In Tab.~\ref{tab:wg1_LOrates} we report the total rates at LO accuracy obtained with the set-up described in Eqs.~(\ref{cut:1}-\ref{cut:3}) with the VBS cuts $m_{\Pj\Pj} > 500 \GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ (see Eq.~(\ref{cut:4})).
The order considered here is the order $\mathcal{O}(\alpha^6)$.
We note that several full predictions are not in statistical agreement.
These are possibly due to too aggressive estimations of statistical uncertainty or ... \MP{To be added}
Nonetheless, all these predictions agree within less than $0.5\%$.
At the level of the cross section, it seems difficult to infer the quality of the the various approximations.
This simply means that the various VBS approximations are not worth than $0.5\%$ at the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.

>>>>

In Tab.~\ref{tab:wg1_LOrates}, we report the total rates at LO accuracy obtained with the set-up described in Eqs.~(\ref{cut:1}-\ref{cut:3}) with the VBS cuts $m_{\Pj\Pj} > 500 \GeV$ and $|\Delta y_{\Pj\Pj}| > 2.5$ (see Eq.~(\ref{cut:4})).
The order considered here is the order $\mathcal{O}(\alpha^6)$.
We note that several full predictions are not in statistical agreement.
These are possibly due to too aggressive estimations of statistical uncertainty or ... \MP{To be added}
Nonetheless, all these predictions agree within less than $0.5\%$.
At the level of the cross section, it seems difficult to infer the quality of the the various approximations.
This simply means that the various VBS approximations are not worth than $0.5\%$ at the level of the fiducial cross section at LO for a typical phase-space volume used by experimental collaborations.

### 2018-02-09 Draft/crosssectionNLO.tex
Lots of corrections and improvements

In Tab.~\ref{tab:wg1_NLOrates}, the cross sections of the various tools at NLO QCD accuracy are presented.
The order considered is $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
In contrast with Tab.~\ref{tab:wg1_LOrates}, the NLO predictions seems to visibly differing according to the approximations used already at the level of the fiducial cross section.

>>>>

In Tab.~\ref{tab:wg1_NLOrates}, the cross sections of the various tools at NLO-QCD accuracy are presented.
The order considered is again the order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$ and the fiducial volume is the one described in Sec.~\ref{subsec:inputpar}.
In contrast with Tab.~\ref{tab:wg1_LOrates}, the NLO predictions are visibly differ according to the approximations used.

### 2018-02-09 Draft/definition.tex
Lots of corrections and improvements

In experimental measurements, special VBS-cuts are designed to enhance the EW contribution over the QCD one.
These cuts are based on the fact that the two contributions have different kinematical behaviour.
The EW contribution is characterised by two jets with large rapidities as well as a large invariant mass.
The two W bosons are mostly produced centrally.
This is in contrast to the QCD contribution which favours jets in the central region.
Therefore, the event selection usually involves rapidity-difference and invariance-mass cuts for the jets.
This will also be discussed in Sec.~\ref{subsec:contributions}.

>>>>

In experimental measurements, special VBS-cuts are designed to enhance the EW contribution over the QCD one.
These cuts are based on the fact that the two contributions have different kinematical behaviour.
The EW contribution is characterised by two jets with large rapidities as well as a large invariant mass.
The two W bosons are mostly produced centrally.
This is in contrast with the QCD contribution which favours jets in the central region.
Therefore, the event selection usually involves rapidity-difference and invariance-mass cuts for the jets.
This will be further discussed in Sec.~\ref{subsec:contributions}.

### 2018-02-09 Draft/description.tex
Lots of corrections and improvements

  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
        Frederix:2016rdc}) for regulating IR singularities. The computations of one-loop amplitudes are carried out by switching dynamically between
        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which
        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
        Hirschi:2016mdz}, or {\sc IREGI}~\cite{ShaoIREGI}, together with an in-house implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}.\\
        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
\begin{verbatim}
> set complex_mass_scheme #1
> import model loop_qcd_qed_sm_Gmu #2
> generate p p > e+ ve mu+ vm j j QCD=0 [QCD] #3
> output #4
\end{verbatim}
  With these commands the complex-mass scheme is turned on {\tt \#1}, then the NLO-capable model is loaded {\tt \#2}\footnote{Despite
            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections
        with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
        and written to disk {\tt \#4}. Because of some internal limitations, which will be lifted in the future version capable of computing both QCD and EW corrections,
        only loops with QCD-interacting particles are generated.
        \MP{Detail of the approximation done, divergent part, assumed to cancel etc.}

@@

  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for matching NLO-QCD calculations with parton showers.
It relies on the user providing the matrix elements and Born phase space, but will automaticaly construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
\MP{Mention the non-clustering for the scale as well as the different running of alphas at NLO.}

\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the general matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
The fast integration is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
The IR divergences appearing in the real corrections are handles with the help of the Catani--Seymour dipole formalism \cite{Catani:1996vz,Dittmaier:1999mb}.
To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg}.
These tools have been successfully used for the computation of NLO corrections for high-multiplicity processes and in particular VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.

>>>>

  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
        Frederix:2016rdc}) for regulating IR singularities. The computations of one-loop amplitudes are carried out by switching dynamically between
        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which
        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
        Hirschi:2016mdz}, or {\sc IREGI}~\cite{ShaoIREGI}, \MP{Is Collier not missing here? I think it made it to one of the default if I am correct} together with an in-house implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}.\\
        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
\begin{verbatim}
> set complex_mass_scheme #1
> import model loop_qcd_qed_sm_Gmu #2
> generate p p > e+ ve mu+ vm j j QCD=0 [QCD] #3
> output #4
\end{verbatim}
  With these commands the complex-mass scheme is turned on {\tt \#1}, then the NLO-capable model is loaded {\tt \#2}\footnote{Despite
            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections
        with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
        and written to disk {\tt \#4}. Because of some internal limitations, which will be lifted in the future version capable of computing both QCD and EW corrections,
        only loops with QCD-interacting particles are generated.
        \MP{Detail of the approximation done, divergent part, assumed to cancel etc.}

@@

  \item The {\sc Powheg-Box}~\cite{Alioli:2010xd,Frixione:2007vw} is a framework for matching NLO-QCD calculations with parton showers.
It relies on the user providing the matrix elements and Born phase space, but will automatically construct FKS \cite{Frixione:1995ms} subtraction terms and the phase space for the real emission.
For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are the similar to those used in {\sc VBFNLO}.
\MP{Mention the non-clustering for the scale as well as the different running of alphas at NLO.}

\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
It can compute arbitrary processes for the LHC at both NLO QCD and EW accuracy in the Standard Model.
This is made possible by the fact that {\sc Recola} can compute arbitrary processes at tree and one-loop level in the Standard Model.
To that end, it relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg} to numerically evaluate the one-loop scalar and tensor integrals.
In addition, the subtraction of the IR divergences appearing in the real corrections has been automatised thanks to the Catani--Seymour dipole formalism for both QCD and QED \cite{Catani:1996vz,Dittmaier:1999mb}.
The code has demonstrated its ability to compute at NLO high multiplicity processes up to $2 \to 7$ \cite{Denner:2015yca,Denner:2016wet}.
In particular the full NLO corrections to VBS and its irreducible background \cite{Biedermann:2016yds,Biedermann:2017bss} have been obtained from this tool.
One key aspect for these high multiplicity processes is the fast integration which is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.

### 2018-02-09 Draft/distributionsLO.tex
Lots of corrections and improvements

In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (top) and the rapidity difference of the two tagging jets (bottom) which are key observables for VBS measurements.
In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over {\sc VBFNLO} \MP{To be changed to Recola}.
For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as from non-resonant configurations are suppressed in the fiducial region.
In general, the agreement is at the level of $1\%$ or below for each bin.
We have checked that the same level of agreement holds for other standard differential distributions such as rapidity, invariant mass, transverse momentum.
This means that at LO, in the fiducial volume, the VBS approximation is good to a per cent.

>>>>

In Fig.~\ref{fig:wg1_mjj-llLO}, we show the distributions in the invariant mass (top) and the rapidity difference of the two tagging jets (bottom) which are key observables for VBS measurements.
In both cases we show the absolute distributions in the upper plot, while the lower plot displays the ratio over {\sc VBFNLO} \MP{To be changed to Recola}.
For both observables we find a relatively good agreement among the various tools, which confirms the fact that contributions from $s$-channel diagrams as well as from non-resonant configurations are suppressed in the fiducial region.
In general, the agreement is at the level of $1\%$ or below for each bin.
We have checked that the same level of agreement holds for other standard differential distributions such as rapidity, invariant mass, or transverse momentum.
This means that at LO, in the fiducial volume, the VBS approximation is good to a per cent.
\MP{Add some comment with respect to the 2D scan.}

### 2018-02-09 Draft/distributionsNLO.tex
Lots of corrections and improvements

Concerning the transverse momentum (top) and rapidity (bottom) of the hardest jet shown in Fig.~\ref{fig:distNLO2}, the situation is rather different.
While {\sc MadGraph5\_aMC@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum.
This is in contrast with {\sc BONSAY} and {\sc POWHEG} which approximate the full computation reasonably well over the whole range and in particular the high transverse-momentum region.
Finally, {\sc VBFNLO} predicts higher rates over the whole range apart around $200\GeV$ where it is in perfect agreement with the complete calculation.
Concerning the rapidity of the hardest jet, {\sc VBFNLO} is in good agreement with {\sc MoCaNLO}+{\sc Recola} in the rapidity range $|y_{j_1}| < 3$.
For larger rapidity, the other codes constitute a better description of the full process at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.

@@

The last set of differential distributions is the invariant mass of the two charged lepton (top) and the Zeppenfeld variable for the anti-muon (bottom).
Concerning the comparison of the predictions, both distributions display a rather similar behaviour.
Indeed, the hierarchy mentioned previously is here respected and enhanced towards high invariant mass or high Zeppenfeld variable.
{\sc MoCaNLO}+{\sc Recola} and {\sc VBFNLO} are in rather good agreement for both distributions for the kinematic range displayed here.
The other three VBS approximations seem to be close to each other.

>>>>

Concerning the transverse momentum (top) and rapidity (bottom) of the hardest jet shown in Fig.~\ref{fig:distNLO2}, the situation is rather different.
While {\sc MadGraph5\_aMC@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum.
This is in contrast with {\sc BONSAY} and {\sc POWHEG} which approximate the full computation reasonably well over the whole range and in particular in the high transverse-momentum region.
Finally, {\sc VBFNLO} predicts higher rates over the whole range apart around $200\GeV$ where it is in perfect agreement with the complete calculation.
Concerning the rapidity of the hardest jet, {\sc VBFNLO} is in good agreement with {\sc MoCaNLO}+{\sc Recola} in the rapidity range $|y_{j_1}| < 3$.
For larger rapidity, the other codes constitute a better description of the full process at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.

@@

The last set of differential distributions is the invariant mass of the two charged lepton (top) and the Zeppenfeld variable for the anti-muon (bottom).
Concerning the comparison of the predictions, both distributions display a rather similar behaviour.
Indeed, the hierarchy mentioned previously is here respected and enhanced towards high invariant mass or high Zeppenfeld variable.
{\sc MoCaNLO}+{\sc Recola} and {\sc VBFNLO} are in rather good agreement for both distributions for the kinematic range displayed here.
The other three VBS approximations are close to each other within few per cent.

### 2018-02-09 Draft/input.tex
Lots of corrections and improvements

For the mass and width of the massive particles, the following values are used:
%
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV.
\end{alignat}
%
The measured on-shell (OS) values for the masses and widths of the W and Z bosons are converted into pole values for the gauge bosons ($V=\PW,\PZ$) according to Ref.~\cite{Bardin:1988xt},
%
\begin{equation}
\begin{split}
        M_V &= \MVOS/\sqrt{1+(\GVOS/\MVOS)^2}\,, \\
   \Gamma_V &= \GVOS/\sqrt{1+(\GVOS/\MVOS)^2}.
\end{split}
\end{equation}
%
The EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj} where
%
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
%
The numerical value of $\alpha$, corresponding to the choice of input parameters is
%
\begin{equation}
 \alpha = 7.555310522369 \times 10^{-3}.
\end{equation}
The CKM-Matrix is assumed to be diagonal, meaning that we neglect mixing between different quark families.
%
The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.

The renormalisation and factorisation scales are set to the dynamical scale
%
\begin{equation}
\label{eq:defscale}
 \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}}.
\end{equation}
%
This choice of scale has been shown to provide stable NLO predictions \cite{Denner:2012dz}.

>>>>

For the mass and width of the massive particles, the following values are used:
%
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV.
\end{alignat}
%
The measured on-shell (OS) values for the masses and widths of the W and Z bosons are converted into pole values for the gauge bosons ($V=\PW,\PZ$) according to Ref.~\cite{Bardin:1988xt},
%
\begin{equation}
\begin{split}
        M_V &= \MVOS/\sqrt{1+(\GVOS/\MVOS)^2}\,, \\
   \Gamma_V &= \GVOS/\sqrt{1+(\GVOS/\MVOS)^2}.
\end{split}
\end{equation}
%
The EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj} where
%
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
%
The numerical value of $\alpha$, corresponding to the choice of input parameters is
%
\begin{equation}
 \alpha = 7.555310522369 \times 10^{-3}.
\end{equation}
The CKM-Matrix is assumed to be diagonal, meaning that the mixing between different quark families is neglected.
The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.

The renormalisation and factorisation scales are set to the dynamical scale
%
\begin{equation}
\label{eq:defscale}
 \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}}.
\end{equation}
%
This choice of scale has been shown to provide stable NLO-QCD predictions \cite{Denner:2012dz}.

### 2018-02-09 Draft/introduction.tex
Lots of corrections and improvements

Vector-boson scattering (VBS) is a class of processes that allow to probe the nature of Higgs-vector-vector couplings and triple and quartic gauge couplings.
It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs boson and can be longitudinally polarized.
The scattering of longitudinally polarized bosons is of particular interest, because the corresponding matrix elements feature both gauge and unitarity cancellations that strongly depend on the actual form of the Higgs sector.
A detailed study of this class of processes will therefore further constrain the Higgs couplings and hint at or exclude non-Standard Model Higgs bosons.

@@

The $\PW^+\PW^+$ scattering is the simplest VBS process to calculate, because of the double-charge structure of the leptonic final state that limits the number of partonic processes and total number of Feynman diagrams for each process.
It also implies that irreducible backgrounds are comparatively small, which make this VBS process experimentally favourable in comparison to \eg to $\PW^+\PW^-$ scattering, which has the largest cross section.
Therefore, the $\PW^+\PW^+$ scattering is an ideal candidate for a detailed study of various theoretical predictions.

In the last few years, several leading order (LO) and next-to-leading order (NLO) computations became available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
The VBS computations all rely on approximations, while recently the complete NLO corrections have been performed~\cite{Biedermann:2017bss}.
It is therefore interesting to infer in details the quality of the various approximations.
Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out.
Preliminary results have already been made public in Ref.~\cite{Anders:2018gfr}.

The hadronic process is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$, which includes the $\PW^+\PW^+$ scattering.
This final state possesses three contributions at LO whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
They are commonly referred to as electroweak (EW), interference, and QCD contributions, respectively.%
\footnote{The EW contribution is sometimes referred to as the VBS contribution even it possesses non-VBS contributions.}
Therefore, the present work starts with a LO study of these three contributions as a function of typical VBS cuts.
This allows to quantify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj$.
This is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.

At NLO, the process possesses four contributions of orders $\mathcal{O}{\left(\alpha^{7}\right)}$, $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
The largest ones are the EW corrections~\cite{Biedermann:2017bss,Biedermann:2016yds} of order $\mathcal{O}{\left(\alpha^{7}\right)}$.
The contribution to the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution and is often referred to as the QCD corrections to the VBS process.
In the following, this order is the one where our comparisons are focused on.
In this article we will refer to it as simply \emph{NLO}.
As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.
In particular, this allows to infer the accuracy of the so-called VBS approximation, which we will define in more detail later.
To our knowledge, such a detailed study was still missing.

>>>>

Vector-boson scattering (VBS) is a class of processes that allow to probe the nature of Higgs-vector-vector couplings and triple and quartic gauge couplings.
It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs boson and can be longitudinally polarised.
The scattering of longitudinally polarised bosons is of particular interest, because the corresponding matrix elements feature both gauge and unitarity cancellations that strongly depend on the actual structure of the Higgs sector.
A detailed study of this class of processes will therefore further constrain the Higgs couplings and hint at or exclude non-Standard Model Higgs bosons.

@@

The $\PW^+\PW^+$ scattering is the simplest VBS process to calculate, because of the double-charge structure of the leptonic final state that limits the number of partonic processes and total number of Feynman diagrams for each process.
It also implies that irreducible backgrounds are comparatively small, which make this VBS process experimentally favourable in comparison to \eg $\PW^+\PW^-$ scattering, which has the largest cross section.
Therefore, the $\PW^+\PW^+$ scattering is an ideal candidate for a detailed study of various theoretical predictions.

In the last few years, several next-to-leading order (NLO) computations became available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
The VBS computations all rely on approximations, while recently the complete NLO corrections have been performed~\cite{Biedermann:2017bss}.
It is therefore interesting to infer in details the quality of the various approximations.
Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out.
Preliminary results of the present study have already been made public in Ref.~\cite{Anders:2018gfr}.

The hadronic process is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$, which includes the $\PW^+\PW^+$ scattering.
This final state possesses three contributions at leading order (LO) whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
They are commonly referred to as electroweak (EW), interference, and QCD contributions, respectively.%
\footnote{The EW contribution is sometimes referred to as the VBS contribution even it possesses non-VBS contributions.}
Therefore, the present work starts with a LO study of these three contributions as a function of typical VBS cuts.
This allows to quantify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj$.
This is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.

At NLO, the process possesses four contributions of orders $\mathcal{O}{\left(\alpha^{7}\right)}$, $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
The largest ones are the EW corrections~\cite{Biedermann:2017bss,Biedermann:2016yds} of order $\mathcal{O}{\left(\alpha^{7}\right)}$.
The contribution to the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution and is often referred to as the QCD corrections to the VBS process.
In the following, this order is the one where our comparisons are focused on.
In this article we will refer to it as simply \emph{NLO}.
As for the LO study, the various predictions are compared at the level of the cross section and differential distributions now at NLO accuracy.
In particular, this allows to infer the accuracy of the so-called VBS approximation, which we will define in more details later.
To our knowledge, such a detailed study was still missing.
